\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{left=1in,right=0.75in,top=1in,bottom=1in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace ABCDEF in the next line with your chosen problem
% and replace 1111111 with your Team Control Number
\newcommand{\Problem}{B}
\newcommand{\Team}{223}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{newtxtext}
\usepackage{hyperref}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{float}
\usepackage{subfigure}
\usepackage[pdftex]{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{url}
\DeclareUnicodeCharacter{0300}{\'{a}}
\lhead{Team \Team}
\rhead{}
\cfoot{}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}{Definition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\graphicspath{{.}}  % Place your graphic files in the same directory as your main document
\DeclareGraphicsExtensions{.pdf, .jpg, .tif, .png}
\thispagestyle{empty}
\vspace*{-16ex}
\centerline{\begin{tabular}{*3{c}}
	\parbox[t]{0.3\linewidth}{\begin{center}\textbf{Problem Chosen}\\ \Large \textcolor{red}{\Problem}\end{center}}
	& \parbox[t]{0.3\linewidth}{\begin{center}\textbf{2024\\ MCM/ICM\\ Summary Sheet}\end{center}}
	& \parbox[t]{0.3\linewidth}{\begin{center}\textbf{Team Control Number}\\ \Large \textcolor{red}{\Team}\end{center}}	\\
	\hline
\end{tabular}}
%%%%%%%%%%% Begin Summary %%%%%%%%%%%
%标题
\begin{center}
	\Huge {Enhancing Taxi Route Planning: A Comprehensive Analysis of ISPL }\\
	\vspace{0.4cm}
	\normalsize\textbf{Summary}
\end{center}
\vspace{0.2cm}

\indent Taxi companies need to consider user preferences reflected in historical path data because the best route during a taxi ride may not necessarily be the shortest route. It is important to take into account both the distance and user preferences in order to determine the optimal route. Assigning weights to paths based on ambiguous user preferences and planning the shortest path under corresponding conditions belongs to a type of an inverse shortest path length problem(ISPL). To address this problem, we introduce edge PageRank to measure road weights and utilize simulated annealing algorithm to find the maximum SIM value.\\
\indent For the first task, we prove by contradiction that the SIM value in example 1 cannot be equal to 1. Additionally, we attempted to assign weights to each edge, \textbf{resulting in a SIM value of 0.75}.\\
\indent For the second task, we first preprocessed the data in Case 1. We placed the data points on a map of Beijing to observe their distribution characteristics and removed duplicate edges and identified edges that did not appear in any of the paths. We then investigated the number of times each edge was traversed in the paths and analyzed the distribution characteristics of the data.Then, we used \textbf{Dijkstra's algorithm} to find the shortest path length for each path. We sorted the paths in ascending order based on their starting and ending points. By processing all paths with the same starting point at once using an array, we significantly reduced the time complexity. Finally, we calculated that \textbf{the SIM value for Case 1 is 0.248971}.\\
\indent For the third task, in our initial model, we used \textbf{road length, road importance (measured by edge PageRank), and straight-line distance} to measure road weights. We calculated the straight-line distance based on the latitude and longitude of the starting and ending points. We calculated \textbf{the maximum SIM value to be 0.273278}. We then conducted further analysis and found that the straight-line distance had little impact on the SIM value. However, we discovered a significant relationship \textbf{between the data point's index and its location}. Therefore, we decided to optimize our model by excluding the straight-line distance, introduceing the edge index into the calculation formula for edge PageRank and adding a constant. Ultimately, we determined \textbf{several parameters, denoted as 26.27088, 0.01172792, and 0.256358}, to calculate the edge weights. It results in \textbf{a maximum SIM value of 0.298223}.\\
\indent For the fourth task,we first compared the optimization rates of the two models in terms of SIM values obtained compared to using length as edge weights. Next, we plotted scatter plots \textbf{comparing the distribution differences between edge weights and edge lengths}, and analyzed the impact of introducing PageRank into the weight calculation.\\
\indent Finally, we conducted \textbf{sensitivity tests} on the resulting model. We selected the parameters \textbf{strides and initial and final temperatures} for testing and found that the model exhibited good stability for different values of these parameters.\\
%关键词
\vspace{0.4cm}
 \textbf{Keywords: }Route Planning\quad Inverse Shortest Path Length \quad Simulated Annealing Algorithm
%%%%%%%%%%% End Summary %%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\pagestyle{fancy}
% Uncomment the next line to generate a Table of Contents
%\tableofcontents 
\newpage
\setcounter{page}{2}
\rhead{Page \thepage~of~25}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%目录
\tableofcontents
\newpage

%正文部分
\input{body/introduction.tex}
\input{body/assumption.tex}
\input{body/notations.tex}
\input{body/model.tex}
\input{body/testing.tex}
\input{body/strengths and weaknesses.tex}
\input{body/reference.tex}
\input{body/appendices.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
\end